---
title: "Assignment 3 - Applying meta-analytic priors"
author: "Riccardo Fusaroli"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assignment 3

In this assignment we do the following:
- we run a Bayesian meta-analysis of pitch variability in ASD, based on previously published literature
- we analyze pitch variability in ASD in two new studies using both a conservative and a meta-analytic prior
- we assess the difference in model quality and estimates using the two priors. 

The questions you need to answer are: What are the consequences of using a meta-analytic prior? Evaluate the models with conservative and meta-analytic priors. Discuss the effects on estimates. Discuss the effects on model quality.
Discuss the role that meta-analytic priors should have in scientific practice. Should we systematically use them? Do they have drawbacks? Should we use them to complement more conservative approaches? How does the use of meta-analytic priors you suggest reflect the skeptical and cumulative nature of science?

```{r}
pacman::p_load(tidyverse, brms, metafor, here, patchwork)
```



# Meta analysis
Step 1: Perform a meta-analysis of pitch variability from previous studies of voice in ASD
- N.B. all you need is in the two intro videos
- the data is available as Ass3_MetaAnalysisData.tsv
```{r}
#loading the data and simple preprocessing
meta <- read_tsv("Ass3_MetaAnalysisData.tsv") %>% 
  mutate(
    PitchVariabilityASD_Mean = as.numeric(PitchVariabilityASD_Mean),
    PitchVariabilityTD_Mean = as.numeric(PitchVariabilityTD_Mean),
    PitchVariabilityASD_SD = as.numeric(PitchVariabilityASD_SD),
    PitchVariabilityTD_SD= as.numeric(PitchVariabilityTD_SD),
  ) %>% 
  subset(!is.na(Paper))
```

- You should calculate Effect size (cohen's d) and Standard Error (uncertainty in the Cohen's d) per each study, using escalc() from the metafor package (also check the livecoding intro)
```{r}
##################################################### COHENS'D USING ESCALC ##########################################
#calculating yi (effect-size) and vi(variance of effect-size) for each paper
meta <- meta %>%  escalc(
  measure = "SMD",
  n1i = TD_N,
  n2i = ASD_N,
  m1i = PitchVariabilityTD_Mean,
  m2i = PitchVariabilityASD_Mean,
  sd1i = PitchVariabilityTD_SD,
  sd2i = PitchVariabilityASD_SD,
  data = meta,
  slab = Paper
)

#changing variance to SE and renaming yi.
meta <- meta %>% 
  mutate(
    StandardError = sqrt(vi)
  ) %>% rename(
    EffectSize = yi
  )
```


- N.B. for the purpose of the assignment we're only interested in getting a meta-analytic effect size for the meta-analytic prior (and not e.g. all the stuff on publication bias). See a brms tutorial here: https://vuorre.netlify.com/post/2016/09/29/meta-analysis-is-a-special-case-of-bayesian-multilevel-modeling/
The formula is EffectSize | se(StandardError) ~ 1 + (1 | Paper). Don't forget prior definition, model checking, etc.
```{r}
########################################## MODELLING META-ANALYSIS ###########################################
#making the formula. Maybe use Population instead of Paper
formula_meta <- bf(EffectSize | se(StandardError) ~ 1 + (1 | Paper))

#chacnking out the priors
get_prior(formula_meta, data = meta, family = gaussian())

#defining the priors
prior_meta <- c(
  prior(normal(0,1), class = Intercept),
  prior(normal(0,0.3), class = sd)
)

#running the brm with priors only
m0_meta_prior <- brm(
  formula = formula_meta,
  data = meta,
  family = gaussian(),
  prior = prior_meta, 
  sample_prior = "only",
  chains = 2,
  cores = 2,
  file = here("Assignment_3", "models_anders", "m0_meta_prior")

)

#doing prior_predictive checks
pp_check(m0_meta_prior, nsamples = 100)
#they seem fine.

#------------------------------ running full model
#running the brm with the data
m0_meta <- brm(
  formula = formula_meta,
  data = meta,
  family = gaussian(),
  prior = prior_meta, 
  sample_prior = T,
  chains = 2,
  cores = 2,
  file = here("Assignment_3", "models_anders", "m0_meta_full")

)
#doing posterior-predictive checks
pp_check(m0_meta, nsamples = 100)
#they seem fine.

#checking the chains. They seem good.
plot(m0_meta)

#checking the output
summary(m0_meta)

```

- N.B. the livecoding video is not perfect, you *can* (but don't have to) improve it: use a t-student likelihood, test the effects of the priors and refine them, check the robustness of results to more or less skeptical priors, etc. 


- Write down the results of the meta-analysis in terms of a prior for step 2.
```{r}
####################################### RESULTS FROM META-ANALYSIS ###################################
meta_mean <- fixef(m0_meta)[[1]]
meta_sd <- fixef(m0_meta)[[2]]
meta_hetero <- 0.35 

# meta effect: mean = -0.46, sd = 0.11, heterogeniety = 0.35
# meaning that pitch-variability is lower in TD than ASD. So level(Diagnosis) = ASD, TD

```


# Loading and inspecting the data 
Step 2: Analyse pitch variability in ASD in two new studies for which you have access to all the trials (not just study level estimates)
- the data is available as Ass3_data.csv. Notice there are 2 studies (language us, and language dk), multiple trials per participant, and a few different ways to measure pitch variability (if in doubt, focus on pitch IQR, interquartile range of the log of fundamental frequency)
- Also, let's standardize the data, so that they are compatible with our meta-analytic prior (Cohen's d is measured in SDs).
```{r}
################################################ READING DATA AND INSPECTING #########################################################
#reading data and scaling Pitch_IQR
df <- read_csv("Ass3_data.csv") %>% 
  mutate(
    Pitch_IQR = scale(Pitch_IQR),
    ID = as.factor(ID),
    Language = as.factor(Language),
    Diagnosis = as.factor(Diagnosis)
  )

#Diagnosis is levelled the same as in the meta-analysis, levels(Diagnosis) = ASD, TD. The effect size from the meta-analysis was negative, meaning that pitch variability is lower in TD. 
levels(df$Diagnosis)

#checking out the outome variable
summary(df$Pitch_IQR)
ggplot(df, aes(x = Pitch_IQR)) + 
  geom_density()
```

- Is there any structure in the dataset that we should account for with random/varying effects? How would you implement that? Or, if you don't know how to do bayesian random/varying effects or don't want to bother, is there anything we would need to simplify in the dataset?
```{r}
#checking out ID-coloumn
ID_dk <- df %>% filter(Language == "dk") %>% summarize(levels(ID)) %>% 
  mutate(
    row = as.factor(row_number())
  )

ID_us <- df %>% filter(Language == "us") %>% summarize(levels(ID)) %>% 
  mutate(
    row = as.factor(row_number())
  )

# it seems that the ID's in both studies (dk and us) are identical. WEIRD. 
# we will make random effects on ID and Language

```


#Building regression models
--------------------------------------------------------------------------------
We want to build the 2 following regression models:
m1: Pitch_IQR ~ 1 + Diagnosis + (1 | ID)
m2: PITCH_IQR ~ 1 + Language + Language:Diagnosis + (1 | Language/ID)

The following chunks are going to be structured like this:
1) Building M1 without meta analysis priors
2) Building M1 with meta-analysis priors
3) Building M2 without meta-analysis priors
4) Building M2 with meta-analysis-priors
5) Model comparison
--------------------------------------------------------------------------------

## M1 Without meta-analysis priors
Step 3: Build a regression model predicting Pitch variability from Diagnosis.
- how is the outcome distributed? (likelihood function). NB. given we are standardizing, and the meta-analysis is on that scale, gaussian is not a bad assumption, but check t-student as well.  Lognormal would require us to convert the prior to that scale.
- how are the parameters of the likelihood distribution distributed? Which predictors should they be conditioned on? Start simple, with Diagnosis only. Add other predictors only if you have the time and energy!
- use a skeptical/conservative prior for the effects of diagnosis. Remember you'll need to motivate it, test its predictions (prior predictive checks), its impact on the posteriors (prior posterior updates checks).
- Evaluate model quality. Describe and plot the estimates. 

```{r}
####################################################### M1 WITHOUT META-ANALYSIS #####################################################
####################################### DEFINING MODEL AND MAKING PRIOR-PREDICTIVE CHECKS ############################################


#defining formula with Diagnosis and varying intercept for ID
f1 <- bf(Pitch_IQR ~ 1 + Diagnosis + (1 | ID))

#checking out priors
get_prior(f1, data = df)

#defining priors
m1_no_meta_priors <- c(
  prior(normal(0,1), class = Intercept),
  prior(exponential(1), class = sigma),
  prior(normal(0,0.2), class = b),
  prior(normal(0, 0.8), class = sd)
)

#running the brm with priors only
m1_no_meta_prior <- brm(
  formula = f1,
  data = df,
  family = gaussian(),
  prior = m1_no_meta_priors, 
  sample_prior = "only",
  chains = 1,
  cores = 1,
  backend = "cmdstanr",
  file = here("Assignment_3", "models_anders", "m1_no_meta_prior")
  )


#doing prior_predictive checks
pp_check(m1_no_meta_prior, nsamples = 100)
#laekker prior
```


```{r}
####################################################### M1 WITHOUT META-ANALYSIS #####################################################
############################################### RUNNING THE MODEL WITH DATA  #########################################################

#running the brm with the data
m1_no_meta <- brm(
  formula = f1,
  data = df,
  family = gaussian(),
  prior = m1_no_meta_priors, 
  sample_prior = T,
  iter = 2000,
  control = list(adapt_delta = 0.99, max_treedepth = 20),
  chains = 4, #change to 1 if it is the first round
  cores = 4, #changer to 1 if it is the first round
  backend = "cmdstanr",
  file = here("Assignment_3", "models_anders", "m1_no_meta_full")
)

#----------------------------------Diagnostics----------------------------------
#No warnings

#Diagnostics
print(m1_no_meta)
#There is a good amount of EES
#Rhat is 1.1 for DiagnosisTD and sd(intercept)

#Checking the chains
plot(m1_no_meta)
#Catterpillars look damn fine

#----------------------------------predictive-checks----------------------------
#doing posterior-predictive checks
pp1 <- pp_check(m1_no_meta, nsamples = 100)
pp1
#Gaussian is maybe not best fit, but works quite fine anyways

#maybe use these???
conditional_effects(m1_no_meta)
plot(conditional_effects(m1_no_meta, spaghetti=T, 
                         method="fitted", nsamples=100), points=T)
plot(conditional_effects(m1_no_meta, spaghetti=T, 
                         method="predict", nsamples=100), points=T)

#---------------------------------prior-posterior update------------------------
#Prior posterior update checks
m1_no_meta_samples <- posterior_samples(m1_no_meta)
m1_no_meta_samples %>% 
  select(c("b_Intercept", "b_DiagnosisTD", "sigma", "prior_Intercept", "prior_b", "prior_sigma")) %>% 
  rename(
    b_sigma = sigma,
    prior_DiagnosisTD = prior_b) %>% 
  pivot_longer(cols = everything(),
               values_to = "value",
               names_to = "distribution"
               ) %>% 
  separate(distribution, c("Distribution", "Parameter"), sep = "_") %>% 
  mutate(Distribution = ifelse(Distribution == "b", "Posterior", "Prior")) %>% 
  ggplot(aes(x = value, fill = Distribution)) + 
  geom_density(alpha = 0.8) +
  facet_wrap(~Parameter, nrow = 1) +
  labs(title = "Prior-posterior updates in M1 without meta-analytic priors")+
  theme_bw()+
  theme(strip.text = element_text(size=15),
        axis.title=element_text(size=15),
        plot.title = element_text(size = 15, face = "bold", hjust = 0.5))


#looking closer at diagnosis
#getting a better look at diagnosis
D1 <- m1_no_meta_samples %>% 
  select(c("b_DiagnosisTD", "prior_b",)) %>% 
  rename(
    prior_DiagnosisTD = prior_b) %>% 
  pivot_longer(cols = everything(),
               values_to = "value",
               names_to = "distribution"
               ) %>% 
  separate(distribution, c("Distribution", "Parameter"), sep = "_") %>% 
  mutate(Distribution = ifelse(Distribution == "b", "Posterior", "Prior")) %>% 
  ggplot(aes(x = value, fill = Distribution)) + 
  geom_density(alpha = 0.8) +
  facet_wrap(~Parameter, nrow = 1) +
  labs(title = "Prior-posterior updates for Diagnosis in M1 without meta-analytic priors")+
  theme_bw()+
  theme(strip.text = element_text(size=15),
        axis.title=element_text(size=15),
        plot.title = element_text(size = 12, face = "bold", hjust = 0.5))
D1
#------------------------------------influential data points and LOO------------
#check for influential data-points
m1_no_meta <- add_criterion(m1_no_meta, "loo", reloo = T)
#2 problematic observation(s) found.

plot(loo(m1_no_meta))
#How to look at this plot?

#below are riccardo notes
# If deviant observations check them in the dataset, are they odd?
# Often deviant observation tell us something important:
## Should we use a different likelihood? e.g. robust regression?
## Should we relax our priors for variation?
## Are there errors in the data?


#-----------------------------------Results-------------------------------------
#checking the output of the model
print(m1_no_meta)
mcmc_plot(m1_no_meta) +
  theme(axis.text.y = element_text(hjust = 0))


#test your hypotheses
hypothesis(m1_no_meta, "DiagnosisTD < 0")
plot(hypothesis(m1_no_meta, "DiagnosisTD < 0"))
#How to interpret all these numbers?
```

## M1 With meta-analysis priors
Step 4: Now re-run the model with the meta-analytic prior
- Evaluate model quality. Describe and plot the estimates. 
- N.B. you need to assess the meta-analytic informed prior (prior pred checks, prior-posterior update checks) and if relevant you can always change it in motivated ways (e.g. too confident, doesn't let the model actually learn from the data, so increase sd)
```{r}
####################################################### M1 WITH META-ANALYSIS ########################################################
####################################### DEFINING MODEL AND MAKING PRIOR-PREDICTIVE CHECKS ############################################

#defining priors for the meta model. Here we use the results from the meta-analys to inform priors.
#we use meta_mean and meta_sd. Should we also use meta_heterogeniety?
m1_meta_priors <- c(
  prior(normal(0,1), class = Intercept),
  prior(exponential(1), class = sigma),
  prior(normal(-0.46, 0.11), class = b),
  prior(normal(0, 0.8), class = sd)
)

#running the brm with priors only
m1_meta_prior <- brm(
  formula = f1,
  data = df,
  family = gaussian(),
  prior = m1_meta_priors, 
  sample_prior = "only",
  chains = 1,
  cores = 1,
  backend = "cmdstanr",
  file = here("Assignment_3", "models_anders", "m1_meta_prior")
  )


#doing prior_predictive checks
pp_check(m1_meta_prior, nsamples = 100)
#priors look the same as m1_no_meta_model because we have only changed priors for b.
```

```{r}
####################################################### M1 WITH META-ANALYSIS ########################################################
############################################### RUNNING THE MODEL WITH DATA  #########################################################

#running the brm with the data
m1_meta <- brm(
  formula = f1,
  data = df,
  family = gaussian(),
  prior = m1_meta_priors, 
  sample_prior = T,
  iter = 2000,
  control = list(adapt_delta = 0.99, max_treedepth = 20),
  chains = 4, #change to 1 if it is the first round
  cores = 4, #changer to 1 if it is the first round
  backend = "cmdstanr",
  file = here("Assignment_3", "models_anders", "m1_meta_full")
)

#------------------------------------diagnostics--------------------------------
#No warnings

print(m1_meta)
#There is a good amount of EES
#Rhat is 1.1 for sd(intercept)

#Checking the chains
plot(m1_meta)
#Catterpillars look damn fine


#---------------------------------predictive-checks-----------------------------
#doing posterior-predictive checks
pp2 <- pp_check(m1_meta, nsamples = 100)
pp2
#Gaussian is maybe not best fit, but works quite fine anyways

#maybe use these???
conditional_effects(m1_meta)
plot(conditional_effects(m1_meta, spaghetti=T, 
                         method="fitted", nsamples=100), points=T)
plot(conditional_effects(m1_meta, spaghetti=T, 
                         method="predict", nsamples=100), points=T)


#--------------------------------prior-posterior-update-------------------------
#Prior posterior update checks
m1_meta_samples <- posterior_samples(m1_meta)
m1_meta_samples %>% 
  select(c("b_Intercept", "b_DiagnosisTD", "sigma", "prior_Intercept", "prior_b", "prior_sigma")) %>% 
  rename(
    b_sigma = sigma,
    prior_DiagnosisTD = prior_b) %>% 
  pivot_longer(cols = everything(),
               values_to = "value",
               names_to = "distribution"
               ) %>% 
  separate(distribution, c("Distribution", "Parameter"), sep = "_") %>% 
  mutate(Distribution = ifelse(Distribution == "b", "Posterior", "Prior")) %>% 
  ggplot(aes(x = value, fill = Distribution)) + 
  geom_density(alpha = 0.8) +
  facet_wrap(~Parameter, nrow = 1) +
  labs(title = "Prior-posterior updates in M1 with meta-analytic priors")+
  theme_bw()+
  theme(strip.text = element_text(size=15),
        axis.title=element_text(size=15),
        plot.title = element_text(size = 15, face = "bold", hjust = 0.5))

#getting a better look at diagnosis
D2 <- m1_meta_samples %>% 
  select(c("b_DiagnosisTD", "prior_b",)) %>% 
  rename(
    prior_DiagnosisTD = prior_b) %>% 
  pivot_longer(cols = everything(),
               values_to = "value",
               names_to = "distribution"
               ) %>% 
  separate(distribution, c("Distribution", "Parameter"), sep = "_") %>% 
  mutate(Distribution = ifelse(Distribution == "b", "Posterior", "Prior")) %>% 
  ggplot(aes(x = value, fill = Distribution)) + 
  geom_density(alpha = 0.8) +
  facet_wrap(~Parameter, nrow = 1) +
  labs(title = "Prior-posterior updates for Diagnosis in M1 with meta-analytic priors")+
  theme_bw()+
  theme(strip.text = element_text(size=15),
        axis.title=element_text(size=15),
        plot.title = element_text(size = 12, face = "bold", hjust = 0.5))
#prior is pushing a ton
D2

#------------------------------influential data points and LOO------------------
#check for influential data-points
m1_meta <- add_criterion(m1_meta, "loo", reloo = T)
 #5 problematic observation(s) found.
#The model will be refit 5 times.

plot(loo(m1_meta))
#How to look at this plot?

#below are riccardo notes
# If deviant observations check them in the dataset, are they odd?
# Often deviant observation tell us something important:
## Should we use a different likelihood? e.g. robust regression?
## Should we relax our priors for variation?
## Are there errors in the data?


#--------------------------------Results----------------------------------------
#checking the output of the model
print(m1_meta)
mcmc_plot(m1_meta) +
  theme(axis.text.y = element_text(hjust = 0))


#test your hypotheses
hypothesis(m1_meta, "DiagnosisTD < 0")
plot(hypothesis(m1_meta, "DiagnosisTD < 0"))
#How to interpret all these numbers?
```


--------------------------------------------------------------------------------
Now we continue to m2
--------------------------------------------------------------------------------

## M2 Without meta-analysis priors


```{r}
####################################################### M2 WITHOUT META-ANALYSIS #####################################################
####################################### DEFINING MODEL AND MAKING PRIOR-PREDICTIVE CHECKS ############################################

#defining formula with 0 and an interaction and varying intercept for ID by language
f2 <- bf(Pitch_IQR ~ 0 + Language + Language:Diagnosis + (1|Language/ID))

#checking out priors
get_prior(f2, data = df)

#defining priors
m2_no_meta_priors <- c(
  prior(exponential(1), class = sigma),
  prior(normal(0, 0.8), class = sd),
  prior(normal(0,0.2), class = b, coef = Languagedk:DiagnosisTD),
  prior(normal(0,0.2), class = b, coef = Languageus:DiagnosisTD),
  prior(normal(0,1), class = b, coef = Languagedk),
  prior(normal(0,1), class = b, coef = Languageus)
)

#running the brm with priors only
m2_no_meta_prior <- brm(
  formula = f2,
  data = df,
  family = gaussian(),
  prior = m2_no_meta_priors, 
  sample_prior = "only",
  chains = 1,
  cores = 1,
  backend = "cmdstanr",
  file = here("Assignment_3", "models_anders", "m2_no_meta_prior")
  )


#doing prior_predictive checks
pp_check(m2_no_meta_prior, nsamples = 100)
#laekker prior
```


```{r}
####################################################### M2 WITHOUT META-ANALYSIS #####################################################
############################################### RUNNING THE MODEL WITH DATA  #########################################################

#running the brm with the data
m2_no_meta <- brm(
  formula = f2,
  data = df,
  family = gaussian(),
  prior = m2_no_meta_priors, 
  sample_prior = T,
  iter = 2000,
  control = list(adapt_delta = 0.99, max_treedepth = 20),
  chains = 4, #change to 1 if it is the first round
  cores = 4, #changer to 1 if it is the first round
  backend = "cmdstanr",
  file = here("Assignment_3", "models_anders", "m2_no_meta_full")
)

#----------------------------------Diagnostics----------------------------------
#No warnings

#Diagnostics
print(m2_no_meta)
#There is a good amount of EES
#Rhat is 1.1 for Languagedk:DiagnosisTD

#Checking the chains
plot(m2_no_meta)
#Catterpillars look damn fine

#----------------------------------predictive-checks----------------------------
#doing posterior-predictive checks
pp3 <- pp_check(m2_no_meta, nsamples = 100)
pp3
#Gaussian is maybe not best fit, but works quite fine anyways

#maybe use these???
conditional_effects(m2_no_meta)
plot(conditional_effects(m2_no_meta, spaghetti=T, 
                         method="fitted", nsamples=100), points=T)
plot(conditional_effects(m2_no_meta, spaghetti=T, 
                         method="predict", nsamples=100), points=T)

#---------------------------------prior-posterior update------------------------
#Prior posterior update checks
m2_no_meta_samples <- posterior_samples(m2_no_meta)
m2_no_meta_samples %>% 
  select(c("b_Languagedk", "b_Languageus", "b_Languagedk:DiagnosisTD", "b_Languageus:DiagnosisTD", "sd_Language__Intercept", "sd_Language:ID__Intercept",
           "prior_b_Languagedk", "prior_b_Languageus", "prior_b_Languagedk:DiagnosisTD", "prior_b_Languageus:DiagnosisTD", "prior_sd_Language", "prior_sd_Language:ID")) %>% 
  rename(
    b_sdLanguage = sd_Language__Intercept,
    b_sdLanguageID = "sd_Language:ID__Intercept",
    prior_Languagedk = prior_b_Languagedk,
    prior_Languageus = prior_b_Languageus,
    "prior_Languagedk:DiagnosisTD" = "prior_b_Languagedk:DiagnosisTD",
    "prior_Languageus:DiagnosisTD" = "prior_b_Languageus:DiagnosisTD",
    prior_sdLanguage = prior_sd_Language,
    prior_sdLanguageID = "prior_sd_Language:ID"
  ) %>% 
  pivot_longer(cols = everything(),
               values_to = "value",
               names_to = "distribution"
               ) %>% 
  separate(distribution, c("Distribution", "Parameter"), sep = "_") %>% 
  mutate(Distribution = ifelse(Distribution == "b", "Posterior", "Prior")) %>% 
  ggplot(aes(x = value, fill = Distribution)) + 
  geom_density(alpha = 0.8) +
  facet_wrap(~Parameter, nrow = 4) +
  labs(title = "Prior-posterior updates in M2 without meta-analytic priors")+
  theme_bw()+
  theme(strip.text = element_text(size=15),
        axis.title=element_text(size=15),
        plot.title = element_text(size = 15, face = "bold", hjust = 0.5)) + 
  xlim(-3,3)


#taking a closer look at the slopes for Diagnosis in both Languages
D3 <- m2_no_meta_samples %>% 
  select(c("b_Languagedk:DiagnosisTD", "b_Languageus:DiagnosisTD", "prior_b_Languagedk:DiagnosisTD", "prior_b_Languageus:DiagnosisTD")) %>% 
  rename(
    "prior_Languagedk:DiagnosisTD" = "prior_b_Languagedk:DiagnosisTD",
    "prior_Languageus:DiagnosisTD" = "prior_b_Languageus:DiagnosisTD",
  ) %>% 
  pivot_longer(cols = everything(),
               values_to = "value",
               names_to = "distribution"
               ) %>% 
  separate(distribution, c("Distribution", "Parameter"), sep = "_") %>% 
  mutate(Distribution = ifelse(Distribution == "b", "Posterior", "Prior")) %>% 
  ggplot(aes(x = value, fill = Distribution)) + 
  geom_density(alpha = 0.8) +
  facet_wrap(~Parameter, nrow = ) +
  labs(title = "Prior-posterior updates for Diagnosis in M2 without meta-analytic priors")+
  theme_bw()+
  theme(strip.text = element_text(size=15),
        axis.title=element_text(size=15),
        plot.title = element_text(size = 12, face = "bold", hjust = 0.5)) 

D3
#------------------------------------influential data points and LOO------------
#check for influential data-points
m2_no_meta <- add_criterion(m2_no_meta, "loo", reloo = T)
#3 problematic observation(s) found.

plot(loo(m2_no_meta))
#How to look at this plot?

#below are riccardo notes
# If deviant observations check them in the dataset, are they odd?
# Often deviant observation tell us something important:
## Should we use a different likelihood? e.g. robust regression?
## Should we relax our priors for variation?
## Are there errors in the data?


#-----------------------------------Results-------------------------------------
#checking the output of the model
print(m2_no_meta)
mcmc_plot(m2_no_meta) +
  theme(axis.text.y = element_text(hjust = 0))


#test your hypotheses
hypothesis(m2_no_meta, "Languagedk:DiagnosisTD < 0")
plot(hypothesis(m2_no_meta, "Languagedk:DiagnosisTD < 0"))

hypothesis(m2_no_meta, "Languageus:DiagnosisTD < 0")
plot(hypothesis(m2_no_meta, "Languageus:DiagnosisTD < 0"))
#How to interpret all these numbers?
```

## M2 With meta-analysis priors
Step 4: Now re-run the model with the meta-analytic prior
- Evaluate model quality. Describe and plot the estimates. 
- N.B. you need to assess the meta-analytic informed prior (prior pred checks, prior-posterior update checks) and if relevant you can always change it in motivated ways (e.g. too confident, doesn't let the model actually learn from the data, so increase sd)
```{r}
####################################################### M2 WITH META-ANALYSIS ########################################################
####################################### DEFINING MODEL AND MAKING PRIOR-PREDICTIVE CHECKS ############################################

#defining priors
m2_meta_priors <- c(
  prior(exponential(1), class = sigma),
  prior(normal(0, 0.8), class = sd), ##### put heterogenoiety here?
  prior(normal(-0.46,0.11), class = b, coef = Languagedk:DiagnosisTD),
  prior(normal(-0.46,0.11), class = b, coef = Languageus:DiagnosisTD),
  prior(normal(0.25,1), class = b, coef = Languagedk),
  prior(normal(0.25,1), class = b, coef = Languageus)
)

#running the brm with priors only
m2_meta_prior <- brm(
  formula = f2,
  data = df,
  family = gaussian(),
  prior = m2_meta_priors, 
  sample_prior = "only",
  chains = 1,
  cores = 1,
  backend = "cmdstanr",
  file = here("Assignment_3", "models_anders", "m2_meta_prior")
)

#doing prior_predictive checks
pp_check(m2_meta_prior, nsamples = 100)
# laekker prior
```

```{r}
####################################################### M2 WITH META-ANALYSIS ########################################################
############################################### RUNNING THE MODEL WITH DATA  #########################################################

#running the brm with the data
m2_meta <- brm(
  formula = f2,
  data = df,
  family = gaussian(),
  prior = m2_meta_priors, 
  sample_prior = T,
  iter = 2000,
  control = list(adapt_delta = 0.99, max_treedepth = 20),
  chains = 4, #change to 1 if it is the first round
  cores = 4, #changer to 1 if it is the first round
  backend = "cmdstanr",
  file = here("Assignment_3", "models_anders", "m2_meta_full")
)

#----------------------------------Diagnostics----------------------------------
#No warnings

#Diagnostics
print(m2_meta)
#There is a good amount of EES

#Checking the chains
plot(m2_meta)
#Catterpillars look damn fine

#----------------------------------predictive-checks----------------------------
#doing posterior-predictive checks
pp4 <- pp_check(m2_meta, nsamples = 100)
pp4
#Gaussian is maybe not best fit, but works quite fine anyways

#maybe use these???
conditional_effects(m2_meta)
plot(conditional_effects(m2_meta, spaghetti=T, 
                         method="fitted", nsamples=100), points=T)
plot(conditional_effects(m2_meta, spaghetti=T, 
                         method="predict", nsamples=100), points=T)

#---------------------------------prior-posterior update------------------------
#Prior posterior update checks
m2_meta_samples <- posterior_samples(m2_meta)
m2_meta_samples %>% 
  select(c("b_Languagedk", "b_Languageus", "b_Languagedk:DiagnosisTD", "b_Languageus:DiagnosisTD", "sd_Language__Intercept", "sd_Language:ID__Intercept",
           "prior_b_Languagedk", "prior_b_Languageus", "prior_b_Languagedk:DiagnosisTD", "prior_b_Languageus:DiagnosisTD", "prior_sd_Language", "prior_sd_Language:ID")) %>% 
  rename(
    b_sdLanguage = sd_Language__Intercept,
    b_sdLanguageID = "sd_Language:ID__Intercept",
    prior_Languagedk = prior_b_Languagedk,
    prior_Languageus = prior_b_Languageus,
    "prior_Languagedk:DiagnosisTD" = "prior_b_Languagedk:DiagnosisTD",
    "prior_Languageus:DiagnosisTD" = "prior_b_Languageus:DiagnosisTD",
    prior_sdLanguage = prior_sd_Language,
    prior_sdLanguageID = "prior_sd_Language:ID"
  ) %>% 
  pivot_longer(cols = everything(),
               values_to = "value",
               names_to = "distribution"
               ) %>% 
  separate(distribution, c("Distribution", "Parameter"), sep = "_") %>% 
  mutate(Distribution = ifelse(Distribution == "b", "Posterior", "Prior")) %>% 
  ggplot(aes(x = value, fill = Distribution)) + 
  geom_density(alpha = 0.8) +
  facet_wrap(~Parameter, nrow = 4) +
  labs(title = "Prior-posterior updates in M2 without meta-analytic priors")+
  theme_bw()+
  theme(strip.text = element_text(size=15),
        axis.title=element_text(size=15),
        plot.title = element_text(size = 15, face = "bold", hjust = 0.5)) + 
  xlim(-3,3)


#taking a closer look at the slopes for Diagnosis in both Languages
D4 <- m2_meta_samples %>% 
  select(c("b_Languagedk:DiagnosisTD", "b_Languageus:DiagnosisTD", "prior_b_Languagedk:DiagnosisTD", "prior_b_Languageus:DiagnosisTD")) %>% 
  rename(
    "prior_Languagedk:DiagnosisTD" = "prior_b_Languagedk:DiagnosisTD",
    "prior_Languageus:DiagnosisTD" = "prior_b_Languageus:DiagnosisTD",
  ) %>% 
  pivot_longer(cols = everything(),
               values_to = "value",
               names_to = "distribution"
               ) %>% 
  separate(distribution, c("Distribution", "Parameter"), sep = "_") %>% 
  mutate(Distribution = ifelse(Distribution == "b", "Posterior", "Prior")) %>% 
  ggplot(aes(x = value, fill = Distribution)) + 
  geom_density(alpha = 0.8) +
  facet_wrap(~Parameter, nrow = ) +
  labs(title = "Prior-posterior updates for Diagnosis in M2 with meta-analytic priors")+
  theme_bw()+
  theme(strip.text = element_text(size=15),
        axis.title=element_text(size=15),
        plot.title = element_text(size = 12, face = "bold", hjust = 0.5)) 

D4

#------------------------------------influential data points and LOO------------
#check for influential data-points
m2_meta <- add_criterion(m2_meta, "loo", reloo = T)
#3 problematic observation(s) found.

plot(loo(m2_meta))
#How to look at this plot?

#below are riccardo notes
# If deviant observations check them in the dataset, are they odd?
# Often deviant observation tell us something important:
## Should we use a different likelihood? e.g. robust regression?
## Should we relax our priors for variation?
## Are there errors in the data?


#-----------------------------------Results-------------------------------------
#checking the output of the model
print(m2_meta)
mcmc_plot(m2_meta) +
  theme(axis.text.y = element_text(hjust = 0))


#test your hypotheses
hypothesis(m2_meta, "Languagedk:DiagnosisTD < 0")
plot(hypothesis(m2_meta, "Languagedk:DiagnosisTD < 0"))

hypothesis(m2_meta, "Languageus:DiagnosisTD < 0")
plot(hypothesis(m2_meta, "Languageus:DiagnosisTD < 0"))
#How to interpret all these numbers?
```

-----------------------------QUESTIONS------------------------------------------
- How should be use the heterogeniety from the meta-analysis?

--------------------------------------------------------------------------------

Step 5: Compare the models
- Plot priors and posteriors of the diagnosis effect in both models

--------------------------------------------------------------------------------
Points about the plot:
-In m1: meta-priors does good, as it pushes Diagnosis in the correct direction
-In m2: meta priors for Diagnosis are good in Languagedk because it pushes in the correct direction
-In m2: meta priors for Diagnosis are not good in Languageus because it pushes in the wrong direction

-It is good to seperate Languagedk and Languageus because Diagnosis have different effects depending on Language. Thus m2 > m1.
--------------------------------------------------------------------------------

```{r}
(D1 + D2) / (D3 + D4)
```


- Compare posteriors between the two models
```{r}
#between m1
pp1 + pp2

#between m2
pp3 + pp4

#maybe use other plots here?
```


- Compare the two models (LOO)
```{r}
##
loo_compare(LanguageDevelopment_m0, LanguageDevelopment_m1)
loo_model_weights(LanguageDevelopment_m0, LanguageDevelopment_m1)
```

- Discuss how they compare and whether any of them is best.

Step 6: Prepare a nice write up of the analysis and answer the questions at the top.







Optional step 7: how skeptical should a prior be?
- Try different levels of skepticism and compare them both plotting the impact on the inferred effect size and using LOO.

Optional step 8: Include other predictors2
- Do age, gender and education improve the model?
- Should they be main effects or interactions?

Optional step 9: generalized linear models
- If you wanted to preserve the lognormal distribution of the pitch variability, what would 
