---
title: "Computational Modeling - Assignment 1"
author: "Riccardo Fusaroli"
date: "07/01/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## In this assignment we learn how to assess rates from a binomial distribution, using the case of assessing your teachers' knowledge of CogSci

N.B. this markdown has 2 parts as it spans 2 weeks of teaching

### First part

You want to assess your teachers' knowledge of cognitive science. "These guys are a bunch of drama(turgist) queens, mindless philosophers, chattering communication people and Russian spies. Do they really know CogSci?", you think.

To keep things simple (your teachers should not be faced with too complicated things):
- You created a pool of equally challenging questions on CogSci
- Each question can be answered correctly or not (we don't allow partially correct answers, to make our life simpler).
- Knowledge of CogSci can be measured on a scale from 0 (negative knowledge, all answers wrong) through 0.5 (random chance) to 1 (awesome CogSci superpowers)

This is the data:
- Riccardo: 3 correct answers out of 6 questions
- Kristian: 2 correct answers out of 2 questions (then he gets bored)
- Daina: 160 correct answers out of 198 questions (Daina never gets bored)
- Mikkel: 66 correct answers out of 132 questions

```{r}
#loading packages
pacman::p_load(tidyverse, rethinking, reshape2)
```

Questions:

1. What's Riccardo's estimated knowledge of CogSci? What is the probability he knows more than chance (0.5) [try figuring this out. if you can't peek into chapters 3.1 and 3.2 and/or the slides]?
- First implement a grid approximation (hint check paragraph 2.4.1!) with a uniform prior, calculate the posterior and plot the results

```{r}
#####################3
# number of points in the grid
dens = 20

bayesian_ric <- tibble(
  pgrid = seq(0, 1, length.out = dens), # making grid approximation
  prior = 1 # stating prior (constant, uniform)
#  prior = ifelse(pgrid < 0.5, 0, 1)
  ) %>% 
  mutate(
  likelihood = dbinom(3, size = 6, prob = pgrid), #calculating likelihood based on binomial distribution
  unstd.post = likelihood * prior, #calculating the un-standardized posterior
  posterior = unstd.post/sum(unstd.post) #calculating the standardized posterior
)

#plotting Riccardo's probability 
ggplot(bayesian_ric, aes(pgrid, posterior)) +
  geom_point() + geom_line() + theme_classic() + geom_line(aes(pgrid, prior/dens, color = 'red')) + xlab('Knowledge of CogSci (pgrid) ') + ylab('Posterior probability')


# The probability that he knows more than by chance is ..
mean(bayesian_ric$pgrid > 0.5)

#50% sandsynlighed..
  
```
The probability that he knows more than by chance is 50% (because he answered 3 out of 6 questions correctly)


- Then implement a quadratic approximation (hint check paragraph 2.4.2!).
- N.B. for the rest of the exercise just keep using the grid approximation (we'll move to quadratic approximations in two classes)

```{r}
################## QUADRATIC APPROXIMATION #####################
ric.qa <- quap(
  alist(
    Co ~ dbinom(Co + Fa, p) , # binomial likelihood 
    p ~ dunif(0,1) # uniform prior
    ), 
data = list(Co = 3, Fa = 3)
)
# display summary of quadratic approximation
precis(ric.qa)

# mean of 0.5, SD = 0.2
```
2. Estimate all the teachers' knowledge of CogSci. Who's best? Use grid approximation. Comment on the posteriors of Riccardo and Mikkel.
2a. Produce plots of the prior, and posterior for each teacher.

```{r}
################### ALL THE TEACHERS - WHO'S BEST? ###################
dens = 100

df_all <- tibble(
  pgrid = seq(0, 1, length.out = dens), # making grid approximation
  prior = 1 # stating prior (constant, uniform)
#  prior = ifelse(pgrid < 0.5, 0, 1)
  ) %>% 
  mutate(
    #calculating likelihood based on binomial distribution --> posterior
  Riccardo_unstd_post = dbinom(3, size = 6, prob = pgrid) * prior, 
  Kristian_unstd_post = dbinom(2, 2, prob = pgrid) * prior,
  Daina_unstd_post = dbinom(160, 198, prob = pgrid) * prior,
  Mikkel_unstd_post = dbinom(66, 132, prob = pgrid) * prior,
  
  # standardize the posteriors
  Riccardo_post = Riccardo_unstd_post/sum(Riccardo_unstd_post),
  Kristian_post = Kristian_unstd_post/sum(Kristian_unstd_post),
  Daina_post = Daina_unstd_post/sum(Daina_unstd_post),
  Mikkel_post = Mikkel_unstd_post/sum(Mikkel_unstd_post)
  ) %>% 
  select(pgrid, prior, Riccardo_post, Kristian_post, Daina_post, Mikkel_post)
  

#### Plotting time

df_all_long <- df_all %>% 
  melt(
    id.vars = c('pgrid', 'prior'), 
    measure.vars = c('Riccardo_post', 'Kristian_post', 'Daina_post', 'Mikkel_post'))


#facet_wrapped version
ggplot(df_all_long, aes(pgrid, value)) + 
  geom_point() + geom_line() + theme_classic() + geom_line(aes(pgrid, prior/dens, color = 'red')) + xlab('Knowledge of CogSci (pgrid) ') + ylab('Posterior probability') + facet_wrap(df_all_long$variable)
  

# a nicer version
ggplot(df_all_long, aes(pgrid, value, colour = variable)) +
 geom_line(size = 1) + theme_minimal() + geom_line(aes(pgrid, prior/dens), color = 'dark blue') + 
  xlab('Proportion of correctly answered questions (pgrid) ') + 
  ylab('Posterior probability') + 
  labs(title = 'Knowledge of CogSci', subtitle = 'How many questions can you get right?') + 
  theme(legend.position = 'bottom', legend.title = element_blank()) + 
  scale_colour_hue(labels = c('Riccardo', 'Kristian', 'Daina', 'Mikkel'))

```
Mikkel's posterior: Lower SD and more 'pointy' distribution.
Riccardo's posterior: Higher SD and less pointy distribution.
We think it is because Mikkel has answered many more questions than Riccardo (132 v. 6). More data equals more certainty about the underlying knowledge/parameter. 

3. Change the prior. Given your teachers have all CogSci jobs, you should start with a higher appreciation of their knowledge: the prior is a normal distribution with a mean of 0.8 and a standard deviation of 0.2. Do the results change (and if so how)?
3a. Produce plots of the prior and posterior for each teacher.

```{r}
################## NEW PRIOR #########################
dens = 100

df_all_2 <- tibble(
  pgrid = seq(0, 1, length.out = dens), # making grid approximation
  prior = dnorm(pgrid, 0.8, 0.2) # SensiblyCenteredAtChance
  ) %>% 
  mutate(
    #calculating likelihood based on binomial distribution --> posterior
  Riccardo_unstd_post = dbinom(3, size = 6, prob = pgrid) * prior, 
  Kristian_unstd_post = dbinom(2, 2, prob = pgrid) * prior,
  Daina_unstd_post = dbinom(160, 198, prob = pgrid) * prior,
  Mikkel_unstd_post = dbinom(66, 132, prob = pgrid) * prior,
  
  # standardize the posteriors
  Riccardo_post = Riccardo_unstd_post/sum(Riccardo_unstd_post),
  Kristian_post = Kristian_unstd_post/sum(Kristian_unstd_post),
  Daina_post = Daina_unstd_post/sum(Daina_unstd_post),
  Mikkel_post = Mikkel_unstd_post/sum(Mikkel_unstd_post)
  ) %>% 
  select(pgrid, prior, Riccardo_post, Kristian_post, Daina_post, Mikkel_post)

df_all_long_2 <- df_all_2 %>% 
  melt(
    id.vars = c('pgrid', 'prior'), 
    measure.vars = c('Riccardo_post', 'Kristian_post', 'Daina_post', 'Mikkel_post'))


# a nicer version
g <- ggplot(df_all_long_2, aes(pgrid, value, colour = variable)) +
 geom_line(size = 1) + theme_minimal() + geom_line(aes(pgrid, prior/dens), color = 'dark blue') +
  xlab('Proportion of correctly answered questions (pgrid) ') + 
  ylab('Posterior probability') + 
  labs(title = 'Knowledge of CogSci', subtitle = 'How many questions can you get right?') + 
  theme(legend.position = 'bottom', legend.title = element_blank()) + 
  scale_colour_hue(labels = c('Riccardo', 'Kristian', 'Daina', 'Mikkel'))


```
How do the results change:
- (ofc) prior is no longer flat
- biggest difference in Riccardo and Kristian's posterior distribution (lower SD)
- the posterior distr. of all the teachers have moved closer to 1.
- the distributions with the least data have changed the most (Ric and Kris)
- question: 'toppunkt' --> mere pointy, more narrow distribution
- it is possible that all of the distributions have become more narrow, but the distributions with the least data are the ones where the change is most visible. 

4. You go back to your teachers and collect more data (multiply the previous numbers by 100). Calculate their knowledge with both a uniform prior and a normal prior with a mean of 0.8 and a standard deviation of 0.2. Do you still see a difference between the results? Why?

```{r}
########### MORE DATA ############
dens = 100

df_all_3 <- tibble(
  pgrid = seq(0, 1, length.out = dens), # making grid approximation
  #prior = 1
  prior = dnorm(pgrid, 0.8, 0.2) # SensiblyCenteredAtChance
  ) %>% 
  mutate(
    #calculating likelihood based on binomial distribution --> posterior
  Riccardo_unstd_post = dbinom(300, size = 600, prob = pgrid) * prior, 
  Kristian_unstd_post = dbinom(200, 200, prob = pgrid) * prior,
  Daina_unstd_post = dbinom(16000, 19800, prob = pgrid) * prior,
  Mikkel_unstd_post = dbinom(6600, 13200, prob = pgrid) * prior,
  
  # standardize the posteriors
  Riccardo_post = Riccardo_unstd_post/sum(Riccardo_unstd_post),
  Kristian_post = Kristian_unstd_post/sum(Kristian_unstd_post),
  Daina_post = Daina_unstd_post/sum(Daina_unstd_post),
  Mikkel_post = Mikkel_unstd_post/sum(Mikkel_unstd_post)
  ) %>% 
  select(pgrid, prior, Riccardo_post, Kristian_post, Daina_post, Mikkel_post)

df_all_long_3 <- df_all_3 %>% 
  melt(
    id.vars = c('pgrid', 'prior'), 
    measure.vars = c('Riccardo_post', 'Kristian_post', 'Daina_post', 'Mikkel_post'))

# a nicer version
ggplot(df_all_long_3, aes(pgrid, value, colour = variable)) +
 geom_line(size = 1) + theme_minimal() + geom_line(aes(pgrid, prior/dens), color = 'dark blue') + 
  xlab('Proportion of correctly answered questions (pgrid) ') + 
  ylab('Posterior probability') + 
  labs(title = 'Knowledge of CogSci', subtitle = 'How many questions can you get right?') + 
  theme(legend.position = 'bottom', legend.title = element_blank()) + 
  scale_colour_hue(labels = c('Riccardo', 'Kristian', 'Daina', 'Mikkel'))

```
*As the amount of data increase, the 'tops' become higher and more pointy. That is, the model is more certain that a teacher will have a given parameter distribution. More narrow distributions. The prior does not have a great effect on the differents distributions, but there is a small difference between using the uniform flat prior and the normally distributed prior.*

5. Imagine you're a skeptic and think your teachers do not know anything about CogSci, given the content of their classes. How would you operationalize that belief?
*choosing a low prior?*

```{r}
dens = 100

df_all_4 <- tibble(
  pgrid = seq(0, 1, length.out = dens), # making grid approximation
  #prior = dnorm(pgrid, 0.2, 005) # low prior
  prior = ifelse(pgrid < 0.5, 0, 1) # nothing below chance?
  ) %>% 
  mutate(
    #calculating likelihood based on binomial distribution --> posterior
  Riccardo_unstd_post = dbinom(30, size = 60, prob = pgrid) * prior, 
  Kristian_unstd_post = dbinom(20, 20, prob = pgrid) * prior,
  Daina_unstd_post = dbinom(1600, 1980, prob = pgrid) * prior,
  Mikkel_unstd_post = dbinom(660, 1320, prob = pgrid) * prior,
  
  # standardize the posteriors
  Riccardo_post = Riccardo_unstd_post/sum(Riccardo_unstd_post),
  Kristian_post = Kristian_unstd_post/sum(Kristian_unstd_post),
  Daina_post = Daina_unstd_post/sum(Daina_unstd_post),
  Mikkel_post = Mikkel_unstd_post/sum(Mikkel_unstd_post)
  ) %>% 
  select(pgrid, prior, Riccardo_post, Kristian_post, Daina_post, Mikkel_post)

df_all_long_4 <- df_all_4 %>% 
  melt(
    id.vars = c('pgrid', 'prior'), 
    measure.vars = c('Riccardo_post', 'Kristian_post', 'Daina_post', 'Mikkel_post'))

# a nicer version
ggplot(df_all_long_4, aes(pgrid, value, colour = variable)) +
 geom_line(size = 1) + theme_minimal() + geom_line(aes(pgrid, prior/dens), color = 'dark blue') + 
  xlab('Proportion of correctly answered questions (pgrid) ') + 
  ylab('Posterior probability') + 
  labs(title = 'Knowledge of CogSci', subtitle = 'How many questions can you get right?') + 
  theme(legend.position = 'bottom', legend.title = element_blank()) + 
  scale_colour_hue(labels = c('Riccardo', 'Kristian', 'Daina', 'Mikkel'))
```

6. Optional question: Can you estimate the difference between Riccardo's estimated knowledge and that of each of the other teachers? Would you deem it credible (that is, would you believe that it is actually different)? 

```{r}
#using the this distribution
g

```
When eye-balling the data, it looks like it is difficult to tell whether Riccardo's estimated knowledge is different from that of the other teachers, since Ric's distribution overlaps all of the other distributions. Based on this, we wouldn't believe that Riccardo's estimated knowledge is different from the other teachers. 

### Second part: Focusing on predictions

Last year you assessed the teachers (darned time runs quick!). Now you want to re-test them and assess whether your models are producing reliable predictions. In Methods 3 we learned how to do machine-learning style assessment of predictions (e.g. rmse on testing datasets). Bayesian stats makes things a bit more complicated. So we'll try out how that works. N.B. You can choose which prior to use for the analysis of last year's data.

Questions to be answered (but see guidance below):
1- Write a paragraph discussing how assessment of prediction performance is different in Bayesian vs. frequentist models
2- Provide at least one plot and one written line discussing prediction errors for each of the teachers.

This is the old data:
- Riccardo: 3 correct answers out of 6 questions
- Kristian: 2 correct answers out of 2 questions (then he gets bored)
- Daina: 160 correct answers out of 198 questions (Daina never gets bored)
- Mikkel: 66 correct answers out of 132 questions

This is the new data:
- Riccardo: 9 correct answers out of 10 questions (then he freaks out about teaching preparation and leaves)
- Kristian: 8 correct answers out of 12 questions
- Daina: 148 correct answers out of 172 questions (again, Daina never gets bored)
- Mikkel: 34 correct answers out of 65 questions

Guidance Tips

1. There are at least two ways of assessing predictions.
2. Last year's results are this year's expectations.
3. Are the parameter estimates changing? (way 1)
4. How does the new data look in last year's predictive posterior? (way 2)
